Design and Implementation of Probabilistic Programming Language Anglican

### 2016-11-27 paper/paper.tex
update

The state (\texttt{\$state}) is threaded through the computation
and contains data used by inference algorithms. \texttt{\$state}
is a Clojure hash map:
\begin{lstlisting}[style=default]
(def initial-state
  "initial program state"
  {:log-weight 0.0,
   :result nil,
   ::mem {},
   ::store nil,
   ... })
\end{lstlisting}
which records inference-relevant information under various keys
such as $\texttt{:log-weight}$ and $\texttt{::mem}$.
The full list of map entries depends on the inference
algorithm. Except for transformation of
\texttt{mem} (which converts a function to one with memoization), 
CPS transformation routines
are not aware of contents of \texttt{\$state}, do not access or
modify it directly, but rather just thread the state unmodified
through the computation. Algorithm-specific handlers of
checkpoints corresponding to the probabilistic forms
(\texttt{sample}, \texttt{observe}) modify the
state and reinject a new state into the computation.

@@

There are three different kinds of inputs to CPS transformation:
\begin{itemize}
    \item literals, which are passed as an argument to the
        continuation unmodified;
    \item value expressions (e.g. the \texttt{fn} form)
        (called \textit{opaque}
        expressions in the code) which must be transformed to
        CPS, but the transformed object is passed to the
        continuation as a whole, opaquely;
    \item general expressions (let's call them
        \textit{transparent}), through which the continuation is
        threaded in an expression-specific way, and can be
        called in multiple locations of the CPS-transformed
        code, such as in all branches of an \texttt{if}
        statement.
\end{itemize}

>>>>

The state (\texttt{\$state}) is threaded through the computation
and contains data used by inference algorithms. \texttt{\$state}
is a Clojure hash map:
\begin{lstlisting}[style=default]
(def initial-state
  "initial program state"
  {:log-weight 0.0,
   :result nil,
   ::mem {},
   ::store nil,
   ... })
\end{lstlisting}
which records inference-relevant information under various keys
such as $\texttt{:log-weight}$ and $\texttt{::mem}$.
The full list of map entries depends on the inference
algorithm. Except for transformation of
the \texttt{mem} form (which converts a function to one with memoization), 
CPS transformation routines
are not aware of contents of \texttt{\$state}, do not access or
modify it directly, but rather just thread the state unmodified
through the computation. Algorithm-specific handlers of
checkpoints corresponding to the probabilistic forms
(\texttt{sample}, \texttt{observe}) modify the
state and reinject a new state into the computation.

@@

There are three different kinds of inputs to CPS transformation:
\begin{itemize}
    \item Literals, which are constant expressions. They
       are passed as an argument to the
        continuation unmodified.
    \item Value expressions such as the \texttt{fn} form
        (called \textit{opaque}
        expressions in the code). They must be transformed to
        CPS, but the transformed object is passed to the
        continuation as a whole, opaquely.
    \item General expressions (which we call
        \textit{transparent} expressions).
        The continuation is threaded through such an expression
        in an expression-specific way, and can be
        called in multiple locations of the CPS-transformed
        code, such as in all branches of an \texttt{if}
        statement.
\end{itemize}
